Title on one or two lines without capitals, except after a colon

### 2020-06-16 Report/Sections/simulation.tex

To test the CarHHMM with STFT, a sequence of 100 marine-animal dives were simulated. The coarse-scale observations $Y$ were set as the duration of each dive, and the fine-scale observations $Y^*$ were set as one dimensional acceleration readings simulated at 50 hertz. Specifically, the following procedure was followed:

@@

	\begin{align*}
		\Gamma &= \begin{pmatrix} 0.4 & 0.6 \\ 0.6 & 0.4 \end{pmatrix} \\
		% 
		&Y_t|X_t \sim Gamma \\
		\bbE(Y_t|X_t = 1) &= 15 s, \quad \bbE(Y_t|X_t = 2) = 60 s \\
		%
		\bbV(Y_t|X_t = 1) &= 25 s^2, \quad \bbV(Y_t|X_t = 2) = 100 s^2
	\end{align*}

	\item Once the dive durations were calculated, for each $t \in \{1, \ldots, 100\}$, dive $t$ was broken into $\lfloor Y_t/2 \rfloor$ 2-second segments (the end of the dive sequence was discarded). Further, each 2-second segment was assigned a behaviour according to a fine-scale Markov chain $X^*_t$, where $X^*_{t,t^*} \in \{1,2\}$ and $t^* \in \{1,101,201,\ldots,100*\lfloor Y_t/2 \rfloor + 1\}$. The parameters of the fine-scale behaviour Markov chain were set to be as follows:
	%
	$$\Gamma^{*(1)} = \begin{pmatrix} 0.25 & 0.75 \\ 0.75 & 025 \end{pmatrix} \qquad 	\Gamma^{*(2)} = \begin{pmatrix} 0.75 & 0.25 \\ 0.25 & 0.75 \end{pmatrix}$$
	%
	where $\Gamma^{*(1)}$ was used for dives where $X_t = 1$ and $\Gamma^{*(2)}$ was used for dives where $X_t = 2$

@@

	\item Finally, $Y^*_{t,t^*:t^*+99}$ is set using the inverse discrete Fourier transform of $\hat{Y}^*_{t,t^*}$:
	$$Y^*_{t,t^*:t^*+99} = IDFT\left(\hat{Y}^*_{t,t^*}\right)$$

@@

Four different models were fit to the generated data shown in figure (\ref{fig:sim_data}):

\begin{enumerate}
    \item A CarHMM with no hierarchical component (CarHMM) using both $Z^{(1)}$ and $Z^{(2)}$ as fine-scale observations
    \item A Hierarchical hidden Markov model with no auto-correlation (HHMM) using both $Z^{(1)}$ and $Z^{(2)}$ as fine-scale observations.
    \item A CarHHMM using $Z^{(1)}$, but not $Z^{(2)}$, as fine-scale observations.
    \item A CarHHMM using both $Z^{(1)}$ and $Z^{(2)}$ as fine-scale observations
\end{enumerate}

Table (\ref{table:emis_dist}) gives the MLE estimates of the parameters for each model above.

>>>>

%!% Have you simulated this only once? I think you would want to do this multiple time and present results across simulations, no?

To test the CarHHMM with STFT, 100 separate sequences of 100 marine-animal dives were simulated. The coarse-scale observations $Y$ were set as the duration of each dive, and the fine-scale observations $Y^*$ were set as one-dimensional acceleration readings simulated at 50 hertz. the specific procedure used to generate data was as follows:

@@

	\begin{align*}
		&\Gamma = \begin{pmatrix} 0.4 & 0.6 \\ 0.6 & 0.4 \end{pmatrix} \\
		% 
		&Y_t|X_t \sim Gamma \\
		&\bbE(Y_t|X_t = 1) = 15 s, \quad \quad \bbE(Y_t|X_t = 2) = 60 s \\
		%
		&\bbV(Y_t|X_t = 1) = 25 s^2, \quad \quad  \bbV(Y_t|X_t = 2) = 100 s^2
	\end{align*}

	\item Once the dive durations were calculated, for each $t \in \{1, \ldots, 100\}$, dive $t$ was broken into $\lfloor Y_t/2 \rfloor$ 2-second segments (the end of the dive sequence was discarded). Further, each 2-second segment was assigned a behaviour according to a fine-scale Markov chain $X^*_t$, where $X^*_{t,t^*} \in \{1,2\}$ and $t^* \in \{1,101,201,\ldots,100\lfloor Y_t/2 \rfloor - 99\}$. The parameters of the fine-scale behaviour Markov chain were set to be as follows:
	%
	$$\Gamma^{*(1)} = \begin{pmatrix} 0.25 & 0.75 \\ 0.75 & 025 \end{pmatrix} \qquad 	\Gamma^{*(2)} = \begin{pmatrix} 0.75 & 0.25 \\ 0.25 & 0.75 \end{pmatrix}$$
	%
	where $\Gamma^{*(1)}$ was used for dives where $X_t = 1$ and $\Gamma^{*(2)}$ was used for dives where $X_t = 2$

@@

	\item Finally, $Y^*_{t,t^*:t^*+99}$ was set using the inverse discrete Fourier transform of $\hat{Y}^*_{t,t^*}$:
	$$Y^*_{t,t^*:t^*+99} = IDFT\left(\hat{Y}^*_{t,t^*}\right)$$

@@

Four different models were fit to the 100 simulated data sets:

\begin{enumerate}
    \item A CarHMM with no hierarchical component using both $Z^{(1)}$ and $Z^{(2)}$ as fine-scale observations (CarHMM).
    \item A Hierarchical hidden Markov model with no auto-correlation using both $Z^{(1)}$ and $Z^{(2)}$ as fine-scale observations (HHMM).
    \item A CarHHMM using $Z^{(1)}$, but not $Z^{(2)}$, as fine-scale observations (CarHHMM1).
    \item A CarHHMM using both $Z^{(1)}$ and $Z^{(2)}$ as fine-scale observations (CarHHMM2).
\end{enumerate}
%
For each model, the following were recorded:
%
\begin{enumerate}
    \item an empirical distribution of the MLE estimates of $\Gamma$ and $\theta$ using the 100 generated data sets generated from true parameters $\Gamma_0$ and $\theta_0$.
    \item a confusion matrix showing the state decoding capabilities of each model across all data sets.
    \item The true coverage of 95\% confidence intervals estimated using the observed information matrix (to see how over- or under- confident our parameter estimates are).
\end{enumerate}
